### 2019-04-29 tii/tex/conclusion.tex
TII commit

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{blue}
Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we evaluate the SCache shuffle optimization by this practical model.
Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
}

>>>>

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{blue}
% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
The benchmark using in evaluations covers the most situations of industrial big-data analysis.
The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last, we evaluate the SCache shuffle optimization by the FRQ model.
% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
}

### 2019-04-29 tii/tex/intro.tex
TII commit

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{blue}
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data \cite{lee2014service, lv2017next}. 
This is because industrial big-data is generated by automated equipment.
However, according to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing. 
A small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to a MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{blue}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{basanta2018efficient, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{blue}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

@@

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing. (Section \ref{model}).
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

>>>>

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{blue}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{blue}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{blue}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{blue}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

@@

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
% By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing (Section \ref{model}).
In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}
